A Formal Model of Checked C

### 2023-01-18 sandp23/appendix.tex

>>>>

\myparagraph{\textbf{ProFTPD}:}
\systemname changes for ProFTPD were lim-
ited was small and exactly encapsulates CVE-2010-4221 by marking the user input to the unsafe function
"pr\_netio\_telnet\_gets()" as tainted. Although we propagate the taintedness of the above function's argument, run-time overhead measured by following the methodology in ~\ref{experimentalsetup} was minimal as the data-flow graph for the pointer was small and thereby, required less pointers to be annotated.

\myparagraph{\textbf{UFTPD}}
\systemname changes for UFTPD were aimed at sandboxing CVE-2020-14149 and CVE-2020-5204. CVE-2020-14149 was recorded as a NULL pointer dereference in the handle\_CWD() which could have led to a DoS in versions before 2.12, thereby, requiring us to sandbox this function. CVE-2020-5204 was recorded as a buffer overflow vulnerability in the handle\_PORT() due to sprintf() which also required us to sandbox this function. Although we could have chosen to only mark the faulty pointers as tainted, we intended to keep our changes more generic.
